PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-11-21 qfenv_paper/qf_environment.tex
Thorough edit part 1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their
star formation only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

Nevertheless, the evolution of the role of environment is a relatively
subtle effect and difficult to study.  Although the history of galaxies
prior to $z\sim 1$ appears to have been one of rapid assembly, since
that time the galaxy population has continued to evolve, but less
dramatically. Although there are detectable changes in the population,
the major classes of galaxies existed at $z\sim 1$, in roughly the
same relative numbers as today (\citealt{bundy06a, borch06a,
taylor09a, Moustakas:2013aa}). Furthermore, at those redshifts we can also
detect the dependence of galaxy properties on environment, with lower
star-formation rate early-type galaxies populating the denser regions
(\citealt{cooper08a, patel09a, kovac10a}).

@@

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments. The most straightforward investigation
would be to directly determine the star-forming properties of galaxies
as a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
end their star formation over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the Prism Multi-object Survey (PRIMUS; \citealt{Coil:2011aa},
\citealt{Cool:2013aa}), the largest available redshift survey covering
the epochs between $0<z<1$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on
the evolution of the quiescent fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\citealt{York:2000aa}).

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
brief summary of the PRIMUS data and the SDSS data used for our sample
selection.  In Section \ref{sec:sfq}, we classify our sample galaxies
as quiescent or star-forming.  In Section \ref{sec:target} we define
our stellar mass complete galaxy sample.  We calculate the environment
using a volume-limited Environment Defining Population in Section
\ref{sec:environment}.  Finally, in Section \ref{sec:edgeeffect}, we
account for edge effects in the surveys.

@@

While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \rm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}). Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS). The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}). Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field. For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs. \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields.

@@

We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Karim:2011aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
\begin{equation}

@@

\end{equation} \label{eq:qsfclass} 

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their
star formation only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

Nevertheless, the evolution of the role of environment is a relatively
subtle effect and difficult to study.  Although the history of galaxies
prior to $z\sim 1$ appears to have been one of rapid assembly, since
that time the galaxy population has continued to evolve, but less
dramatically. Although there are detectable changes in the population,
the major classes of galaxies existed at $z\sim 1$, in roughly the
same relative numbers as today (\citealt{bundy06a, borch06a,
taylor09a, Moustakas:2013aa}). Furthermore, at those redshifts we can also
detect the dependence of galaxy properties on environment, with lower
star-formation rate early-type galaxies populating the denser regions
(\citealt{cooper08a, patel09a, kovac10a}).
% Mention something about the build up of the red sequence?

@@

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments. The most straightforward investigation
would be to directly determine the star-forming properties of galaxies
as a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
end their star formation over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the PRIism MUlti-object Survey (PRIMUS; \citealt{Coil:2011aa},
\citealt{Cool:2013aa}), the largest available redshift survey covering
the epochs between $0<z<1$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on
the evolution of the quiescent fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to robustly measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\citealt{York:2000aa}).

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
brief summary of the PRIMUS data and the SDSS data used for our sample
selection. In Section \ref{sec:target} we define our stellar mass complete galaxy sample.  
Then, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming. 
We calculate the environment
using a volume-limited Environment Defining Population in Section
\ref{sec:environment}.  Finally, in Section \ref{sec:edgeeffect}, we
account for edge effects in the surveys.

@@

While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \rm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}). Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS). The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}). Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field. For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs. \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields. Furthermore, we derive the {\em K-corrections} from the photometry using \texttt{K-correct} (v4.2; \citealt{Blanton:2007aa}).

@@

We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Williams:2009aa, Karim:2011aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
\begin{equation} \label{eq:qsfclass} 

@@

\end{equation} 
